Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-17 paper/paper.tex
Improve title of the paper
Make flow image show in the pdf
Add analyse subsection for paper

\title{Measuring Software Ticket Quality using Statistical Analysis}
\author{Andrei-Mihai Nicolae}
\matricnum{2147392}

@@

@@

In this research paper, we present and discuss our findings after running a statistical analysis 
on over 300,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
from a Jira instance, analyze them, generate plots and run statistical tests.

@@

\section{Building the Data Set}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.3]{images/flow.png}
\end{center}
\caption{\label{fig-eg}Flow of the whole application.}
\end{figure*}

The first step to building the data set was to create a tool that was able to execute all the commands that we required:
fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
we decided that Go was the best way to go for various reasons:
  \begin{itemize}
    \item it is designed with simplicity in min, thus making it easier for others who might join the project to read 
    and understand the codebase;
    \item it is compiled, statically typed, which implies that it is a much faster candidate than other interpreted languages
    such as Ruby or Python;
    \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
  \end{itemize}

Figure \ref{} The following two subsections will describe in detail how the process of building the data set was undergone.

@@

In terms of projects selected, we have opted for the Apache Software Foundation which open-sourced some of the most popular
software applications. Moreover, they have all their projects' issue tracking systems hosted on Jira, thus we could also 
achieve consistency easier.

@@

>>>>

\title{Measuring Software Ticket Quality using Quantitative Data Analysis}
\author{Andrei-Mihai Nicolae}
\matricnum{2147392}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{images/flow.pdf}
\end{center}
\caption{\label{fig-eg}Application flow of the Go tool.}
\end{figure*}

@@

In this research paper, we present and discuss our findings after running a quantitative data analysis 
on over 300,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
from a Jira instance, analyze them, generate plots and run statistical tests.

@@

\section{Building the Data Set}
The first step towards building the data set was to create a tool that was able to execute all the commands that we required:
fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
we decided that Go was the best way to go for various reasons:
  \begin{itemize}
    \item it is designed with simplicity in min, thus making it easier for others who might join the project to read 
    and understand the codebase;
    \item it is compiled, statically typed, which implies that it is a much faster candidate than other interpreted languages
    such as Ruby or Python;
    \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
  \end{itemize}

Then, we split our tool into four main commands: \emph{store}, \emph{analyse}, \emph{plot} and \emph{stats}. They all 
follow the flow shown in figure \ref{fig-eg} and complete the whole application cycle, in the end producing a database 
of analysed tickets, as well as plots and statistics for investigating correlations, saved on the filesystem.

In the following two subsections we describe how we designed and implemented the commands mentioned above.

@@

We have interacted with the Jira Server REST API which has very good documentation written by the Atlassian team. After getting
familiar with all the features the REST API offers, we have opted for getting paginated issues from the server, which means 
slicing the whole set of tickets into multiple smaller arrays to improve performance and reduce the load on the server. We also
specified to Jira exactly what set of issue fields to return and, eventually, while responses were retrieved from the instance,
we began storing them into our Bolt DB instance. The way we chose to store them was to set the issue key (i.e. unique 
identifier that differentiates a ticket from all others across all projects inside a Jira instance) as the key of the pair and
the value is the whole representation of an issue (e.g. attachments, story points, priority) as a JSON encoded value. This
helped us reduce the size of the database once we reached hundreds of thousands of tickets.

@@

Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
fetches all the issues in the database. Then, it runs in parallel the \emph{seven types of analysis}:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket;
  \item \emph{stack traces} - runs complex regex for detecting stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  having many words or comments decreases or increases Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 is completely negative, 1 is completely 
  positive).
\end{itemize}

Implementation wise, the application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
but heavy on resource utilization) or slices them into smaller arrays to get processed afterwards (harder to parse as it 
eventually requires re-creation of the whole array of tickets before inserting back into the database, but it is much 
lighter on computing power). After having the tickets available, we start looping through them and perform all 
analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
its corresponding field in the ticket struct and subsequently stored back in the database. We chose this approach because 
we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
already available there. Moreover, for external analysis such as hitting Google Cloud Platform APIs, there are costs for 
running the analysis, thus in this way we drastically reduce overall costs for the project.

\subsection{Plot and Statistical Tests}
